A recipe for extremely reproducible enrichment analysis (and why we need it)

### 2023-12-05 manuscript/manuscript.Rmd
slight edits

grid()
text(0.7,1:7-0.5,labels=score1)
text(1.9,1:10-0.5,labels=score2)
text(3.1,1:3-0.5,labels=score3)

@@

| 2.PMC6368841: Figure 3 A - D | A. Only GO Terms were the similar as the paper. The FDR values are inconsistent. However, the paper should have clearly mentioned the different tools under figure captions to bring more clarity of the terms obtained by respective tools like DAVID and ClusterProfiler. The KEGG terms do not come up in DAVID at all. B. No | **3 (high).** 3 (high). The article receives a score of 3 solely based on GO results. GO results from the original manuscript are somewhat similar to reproduced analysis in DAVID. The FDR values however are inconsistent. The list of genes as input into DAVID analysis is unclear. The paper should have mentioned that both up and down-regulated proteins were considered for DAVID analysis. Another important question is why were two different tools used for GO and KEGG when both can be performed in DAVID or clusterprofiler? |

>>>>

grid()
text(0.7,1:7-0.5,labels=score1)
text(1.9,1:9-0.5,labels=score2)
text(3.1,1:4-0.5,labels=score3)

@@

| 2.PMC6368841: Figure 3 A - D | A. Only GO Terms were the similar as the paper. The FDR values are inconsistent. However, the paper should have clearly mentioned the different tools under figure captions to bring more clarity of the terms obtained by respective tools like DAVID and ClusterProfiler. The KEGG terms do not come up in DAVID at all. B. No | **3 (high).** The article receives a score of 3 solely based on GO results. GO results from the original manuscript are somewhat similar to reproduced analysis in DAVID. The FDR values however are inconsistent. The list of genes as input into DAVID analysis is unclear. The paper should have mentioned that both up and down-regulated proteins were considered for DAVID analysis. Another important question is why were two different tools used for GO and KEGG when both can be performed in DAVID or clusterprofiler? |
